Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-10-05 Paper.tex
Copied and pasted a formula with tiny in math mode to l. 2097 to see if it will pick up in the Travis CI build.
Changing tabu to tabularx
Retyping lines 2095–2096, math with tiny at beginning of l. 2097.
Definition of e in signing transactions

We assert the functions $\mathtt{\small ECDSAPUBKEY}$, $\mathtt{\small ECDSARECOVER}$ and $\mathtt{\small ECDSASIGN}$. These are formally defined in the literature, \eg by \cite{ECDSAcerticom} and \cite{ECDSAWikipedia}. \footnote{For the former citation, refer to section 6.2 for ECDSAPUBKEY, and section 7 for ECDSASIGN and ECDSARECOVER.} %(assuming that the former is for signature generation and the latter is for signature verification)
\begin{eqnarray}
\mathtt{\small ECDSAPUBKEY}(p_r \in \mathbb{B}_{32}) & \equiv & p_u \in \mathbb{B}_{64} \\
\mathtt{\small ECDSASIGN}(e \in \mathbb{B}_{32}, p_r \in \mathbb{B}_{32}) & \equiv & (v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) \\
\mathtt{\small ECDSARECOVER}(e \in \mathbb{B}_{32}, v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) & \equiv & p_u \in \mathbb{B}_{64}
\end{eqnarray}

Where $p_u$ is the public key, assumed to be a byte array of size 64 (formed from the concatenation of two positive integers each $< 2^{256}$) and $p_r$ is the private key, a byte array of size 32 (or a single positive integer in the aforementioned range)\hypertarget{v}{. It is assumed that $v$ is the `recovery id', a 1 byte value specifying the sign and finiteness of the curve point; this value is in the range of $[27, 30]$, however we declare the upper two possibilities, representing infinite values, invalid.}

@@

\section{Ethash}\label{app:ethash}
\subsection{Definitions}
We employ the following definitions:$\mathtt{\tiny KEC}\big(\mathtt{\tiny RLP}\big( () \big)\big)$

%\begin{tabularx}{\textwidth}{lrX}
\begin{tabu}{X[,l]X[,r]X[,l]}
\toprule
Name & Value & Description \hypertarget{Jwordbytes}{} \\
\midrule
$J_{\mathrm{wordbytes}}$ & 4  & This is the bytes in a word.\hypertarget{Jdatasetinit}{}\\
$J_{\mathrm{datasetinit}}$ & $2^{30}$ & This is the bytes in the dataset at genesis. \hypertarget{Jdatasetgrowth}{} \\
$J_{\mathrm{datasetgrowth}}$ & $2^{23}$ & This is the dataset growth per epoch. \hypertarget{Jcacheinit}{}\\
$J_{\mathrm{cacheinit}}$ & $2^{24}$ & This is the bytes in the cache at genesis.\hypertarget{Jcachegrowth}{}\\
$J_{\mathrm{cachegrowth}}$ & $2^{17}$ & This is the cache growth per epoch.\hypertarget{Jepoch}{}\\
$J_{\mathrm{epoch}}$ & 30000 & This is the blocks per epoch.\hypertarget{Jmixbytes}{}\\
$J_{\mathrm{mixbytes}}$ & 128 & This is the mix length in bytes.\hypertarget{Jhashbytes}{}\\
$J_{\mathrm{hashbytes}}$ & 64 & This is the hash length in bytes.\hypertarget{Jparents}{}\\
$J_{\mathrm{parents}}$ & 256 & This is the number of parents of each dataset element.\hypertarget{Jcacherounds}{}\\
$J_{\mathrm{cacherounds}}$ & 3 & This is the number of rounds in cache production.\hypertarget{Jaccesses}{}\\
$J_{\mathrm{accesses}}$ & 64 & This is the number of accesses in a hashimoto loop.\\
\bottomrule
\end{tabu}
%\end{tabularx}

>>>>

We assert the functions $\mathtt{\small ECDSAPUBKEY}$, $\mathtt{\small ECDSARECOVER}$ and $\mathtt{\small ECDSASIGN}$. These are formally defined in the literature, \eg by \cite{ECDSAcerticom} and \cite{ECDSAWikipedia}. \footnote{For the former citation, refer to section 6.2 for ECDSAPUBKEY, and section 7 for ECDSASIGN and ECDSARECOVER.} %(assuming that the former is for signature generation and the latter is for signature verification)
\begin{eqnarray}
\mathtt{\small ECDSAPUBKEY}(p_r \in \mathbb{B}_{32}) & \equiv & p_u \in \mathbb{B}_{64} \\
\ e = \mathtt{\small HASH}(m) \\
\mathtt{\small ECDSASIGN}(e \in \mathbb{B}_{32}, p_r \in \mathbb{B}_{32}) & \equiv & (v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) \\
\mathtt{\small ECDSARECOVER}(e \in \mathbb{B}_{32}, v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) & \equiv & p_u \in \mathbb{B}_{64}
\end{eqnarray}

Where $p_u$ is the public key, assumed to be a byte array of size 64 (formed from the concatenation of two positive integers each $< 2^{256}$) and $p_r$ is the private key, a byte array of size 32 (or a single positive integer in the aforementioned range). $e$ is the hash of the message $m$, using some cryptographic hash function such as SHA-3.\hypertarget{v}{It is assumed that $v$ is the `recovery id', a 1 byte value specifying the sign and finiteness of the curve point; this value is in the range of $[27, 30]$, however we declare the upper two possibilities, representing infinite values, invalid.}

@@

\section{Ethash}\label{app:ethash}
\subsection{Definitions}
We employ the following definitions:

%\begin{tabu}{X[,l]X[,r]X[,l]}
\begin{tabularx}{\textwidth}{lrX}
\toprule
Name & Value & Description \hypertarget{Jwordbytes}{} \\
\midrule
$J_{\mathrm{wordbytes}}$ & 4  & This is the bytes in a word.\hypertarget{Jdatasetinit}{}\\
$J_{\mathrm{datasetinit}}$ & $2^{30}$ & This is the bytes in the dataset at genesis. \hypertarget{Jdatasetgrowth}{} \\
$J_{\mathrm{datasetgrowth}}$ & $2^{23}$ & This is the dataset growth per epoch. \hypertarget{Jcacheinit}{}\\
$J_{\mathrm{cacheinit}}$ & $2^{24}$ & This is the bytes in the cache at genesis.\hypertarget{Jcachegrowth}{}\\
$J_{\mathrm{cachegrowth}}$ & $2^{17}$ & This is the cache growth per epoch.\hypertarget{Jepoch}{}\\
$J_{\mathrm{epoch}}$ & 30000 & This is the blocks per epoch.\hypertarget{Jmixbytes}{}\\
$J_{\mathrm{mixbytes}}$ & 128 & This is the mix length in bytes.\hypertarget{Jhashbytes}{}\\
$J_{\mathrm{hashbytes}}$ & 64 & This is the hash length in bytes.\hypertarget{Jparents}{}\\
$J_{\mathrm{parents}}$ & 256 & This is the number of parents of each dataset element.\hypertarget{Jcacherounds}{}\\
$J_{\mathrm{cacherounds}}$ & 3 & This is the number of rounds in cache production.\hypertarget{Jaccesses}{}\\
$J_{\mathrm{accesses}}$ & 64 & This is the number of accesses in a hashimoto loop.\\
\bottomrule
\end{tabularx}
%\end{tabu}
